Using a Two-Layer Neural Network and Physicochemical Properties to Classify Glass for Forensic Analysis

### 2017-06-30 Paper/paper.tex
Code edits

%Widrow and Hoff's learning rule suffered from the same disadvantage. When we have more complicated decision boundaries we are trying to implement and have multiple layers, a more robust learning rule ought to be used. Since then, multilayer perceptrons trained by the backpropagation algorithm have become the most popular neural network. \cite{hagan2014}.

\subsection{Training Algorithm}
\label{sec4.2}
We chose to use the Scaled Conjugate Gradient (SCG) algorithm to train our network as it is very efficient for pattern recognition problems. For multi-layer networks, the Levenberg-Marquardt algorithm is often used, but it does not work well for pattern recognition as the transfer function in the output layer is operating outside the linear region. The scaled conjugate gradient algorithm is a special type of backpropagation. In backpropagation, we adjust the weights in the direction of steepest descent...

>>>>

Widrow and Hoff's Least Mean Square (LMS) learning rule suffered from the same disadvantage as Rosenblatt's, but it has since been generalized. The generalization of the LMS learning rule is referred to as \emph{backpropagation} and we commonly use it to train multi-layer perceptron networks \cite{hagan2014}.

\subsection{Training Algorithm}
\label{sec4.2}
We chose to use the Scaled Conjugate Gradient (SCG) algorithm in MATLAB to train our network as it is very efficient for pattern recognition problems. For multi-layer networks, the Levenberg-Marquardt algorithm is often used, but it does not work well for pattern recognition as the transfer function in the output layer is operating outside the linear region. The scaled conjugate gradient algorithm is a special type of backpropagation. For the replication of the network in Python, we use standard backpropagation.

The implementation of backpropagation can be broken down into three steps: 
\begin{enumerate}
\item Propagate the input forward through the network
\item Propagate the sensitivities backward through the network
\item Update the weights and biases using the approximate steepest descent rule
\end{enumerate}

\subsubsection{Forward Propagation}
